### 2022-05-06 GB_Simulation_3Species.Rmd
Updated survey for GB strata

  #load increase temp data from Mars
  load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_IncPop_ConstTemp_environment.RData")

@@

nCoresToUse <- 6

@@

>>>>

  #load increase temp data from Mars
  load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_IncPop_IncrTemp_environment.RData")

@@

nCoresToUse <- 5

@@

#save results
save.image("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_IncPop_IncrTemp_RESULTS.RData")
